Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-18 draft.tex
some improvements

>>>>

\section*{Theorem 8.1}

\noindent \textbf{Theorem 8.1 (Discrete Poincaré inequality).} There holds
\begin{align*}
    \|g\|^2_{0,\Omega} 
    \leq 
    C_P |g|^2_{1,T} 
    + 
    \frac{4}{|\Omega|} \left( \int_{\Omega} g(x) \, dx \right)^2
        \quad 
    \forall g \in W(T_h), \forall h > 0
\end{align*}
with
\begin{align*}
C_P = 4C_d C_\Omega \frac{C_{d,T}}{\kappa_T} [\text{diam}(\Omega)]^2 + 8c_d h^2,
\end{align*}
where \(C_\Omega\) is given by (27) when \(\Omega\) is convex and by (28) otherwise, \(C_{d,T}\) is given by (12) when Assumption (B) is satisfied and by (15) in the general case, \(c_d\) is given by (22), and \(C_d\) is given by (26).
\\

\noindent Obviously
\begin{align*}
    \|g\|_{0,\Omega} 
    \leq 
    \|g - I(g)\|_{0,\Omega} + \|I(g)\|^2_{0,\Omega}
    ,
\end{align*}
\begin{align*}
    \|g\|^2_{0,\Omega} 
    &\leq 
    2\|g - I(g)\|^2_{0,\Omega} + 2\|I(g)\|^2_{0,\Omega} 
    ,
    \|g\|_{0,\Omega} 
    &\leq
    \sqrt{2}
    \sqrt{ \|g - I(g)\|^2_{0,\Omega} + 2\|I(g)\|^2_{0,\Omega} }
    .
\end{align*}
We apply the cellwise local approximation estimate, which coincides with the cellwise Poincare inequality:
\begin{align*}
    \|g - I(g)\|_{0,\Omega}
    &\leq 
    \frac{ h_T }{\pi}
    \| \nabla_\calT g \|_{0,\Omega}
    ,
    \|g - I(g)\|_{0,\Omega}
    &\leq 
    \frac{ h_T }{\pi}
    \| \nabla_\calT g \|_{0,\Omega}
    .
\end{align*}

### 2024-06-18 main.tex
fixes
some improvements

% Title, authors, and affiliations
\title{Poincar\'e--Friedrichs constants over triangulated domains}
\author{TCF, MWL, MV}

@@

A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation}, if it satisfies the following conditions: 
(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
% (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$. 
The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that complex.\footnote{We warn the reader that simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes.} 
We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is defined as the union 
\[
    \underlying{\calT} := \bigcup_{ T \in \calT } T
    .
\]
We call a set \textit{trianguable} if it is the underlying set of some triangulation.

@@

Suppose that $\calT$ is an $n$-dimensional simplicial complex and we have an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$.
For any enumeration, we call 
\[
    I_m 
    := 
    \big( 
        T_{0} \cup T_{1} \cup \dots \cup T_{m} 
    \big) 
    \cap 
    T_{m+1}
\]
be the $m$-th \textit{interface set}. 
% Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
We call the enumeration a \emph{shelling} if each interface $I_m$ is a manifold of dimension $n-1$.

@@

    Since $\calT$ triangulates a $2$-disk,
    it contains a good triangle $T$. 
    If $T$ has three edges in the boundary, then $T = M$ and we are trivially done. 
    If $T$ intersects with the boundary in exactly one or two edges, 
    then $\overline{M \setminus T}$ is still a topological $2$-disk.
    Letting $\calT'$ be the triangulation obtained by removing $T$,
    we have another triangulation of the $2$-disk that intersects $T$ only at either two or one edges.
    Any shelling of $\calT'$ can be extended to a shelling of $\calT$.
%     Let $\calT$ be a simplicial $2$-disk. 
%     If $\calT$ contains only one triangle, then there is nothing to show. 
%     Otherwise, there exists at least one triangle $T$ that touches the boundary of the disk at either one or two edges 
%     {\color{red}Needs proof}.

%     Now let $\calS$ be any simplicial $2$-sphere. 
%     By removing any triangle $S \in \calS$, we obtain a simplicial $2$-disk, which is shellable. 
%     Any of its shellings can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
\end{proof}

@@

\begin{example}
    Not all trianguable sets admit a triangulation that is also shellable. 
    Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
    We refer to~\cite[Example 8.9]{ziegler2012lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions.

>>>>

% Title, authors, and affiliations
\title{Poincar\'e--Friedrichs constants over triangulated domains}
\author{Th\'eophile Chaumont-Frelet, Martin Werner Licht, Martin Vohral\'ik}

@@

A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation}, if it satisfies the following conditions: 
(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
% (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$. 
The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that complex.\footnote{We warn the reader that simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes.} 
We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is defined as the union 
\begin{align*}
    \underlying{\calT} := \bigcup_{ T \in \calT } T
    .
\end{align*}
We call a set \textit{trianguable} if it is the underlying set of some triangulation.

@@

Suppose that $\calT$ is an $n$-dimensional simplicial complex and we have an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$.
For any enumeration, we call 
\begin{align*}
    I_m 
    := 
    \big( 
        T_{0} \cup T_{1} \cup \dots \cup T_{m} 
    \big) 
    \cap 
    T_{m+1}
\end{align*}
be the $m$-th \textit{interface set}. 
% Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
We call the enumeration a \emph{shelling} if each interface $I_m$ is a manifold of dimension $n-1$.

@@

    Since $\calT$ triangulates a $2$-disk,
    it contains a good triangle $T$. 
    If $T$ has three edges in the boundary, then $T = M$ and we are trivially done. 
    If $T$ intersects with the boundary in exactly one or two edges, 
    then $\overline{M \setminus T}$ is still a topological $2$-disk.
    Letting $\calT'$ be the triangulation obtained by removing $T$,
    we have another triangulation of the $2$-disk that intersects $T$ only at either two or one edges.
    Any shelling of $\calT'$ can be extended to a shelling of $\calT$.
%     Let $\calT$ be a simplicial $2$-disk. 
%     If $\calT$ contains only one triangle, then there is nothing to show. 
%     Otherwise, there exists at least one triangle $T$ that touches the boundary of the disk at either one or two edges 
%     {\color{red}Needs proof}. 
%   
%     Now let $\calS$ be any simplicial $2$-sphere. 
%     By removing any triangle $S \in \calS$, we obtain a simplicial $2$-disk, which is shellable. 
%     Any of its shellings can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
\end{proof}

@@

\begin{remark}
    Not all trianguable sets admit a triangulation that is also shellable. 
    Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
    We refer to~\cite[Example 8.9]{ziegler2012lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions.
